Estimating Output Loss due to being Unrecognized as States

### 2019-03-11 paper/paper.tex
Cite papers that use nighttime light to observe economic performance #54

This study contributes to three strands of the literature. 
First, the recent literature on the role of states in economic development focuses on the impacts of state capacity (Besley and Persson 2011, Acemoglu et al.\ 2015). 
However, state capacity is only one side of sovereign states. 
The other side is international recognition, which has been ignored by economists. 
This study fills this gap in the literature of economics.

@@

Finally, the political science literature on unrecognized states focuses on their consequences on domestic politics.
Economic impacts are relatively understudied.%
\footnote{
	An exception is Witmer and O'Loughlin (2011), who also use nighttime light data to gauge the impact of wars in towns in Georgia and South Ossetia. Our study differs in the coverage of study areas and in the recovery of economic growth from light data. 
} 
Our study complements this strand of the literature to understand the issue of unrecognized states.

@@

>>>>

This study contributes to four strands of the literature. 
First, the recent literature on the role of states in economic development focuses on the impacts of state capacity (Besley and Persson 2011, Acemoglu et al.\ 2015). 
However, state capacity is only one side of sovereign states. 
The other side is international recognition, which has been ignored by economists. 
This study fills this gap in the literature of economics.

@@

Third, the political science literature on unrecognized states focuses on their consequences on domestic politics.
Economic impacts are relatively understudied.%
\footnote{
	An exception is Witmer and O'Loughlin (2011), who also use nighttime light data to gauge the impact of wars in towns in Georgia and South Ossetia. Our study differs in the coverage of study areas and in the recovery of economic growth from light data. 
} 
Our study complements this strand of the literature to understand the issue of unrecognized states.

Finally, our study also relates to those who use nighttime light to observe economic performance for countries with poor data: Michalopoulos and Papaioannou (2013, 2014) and Storeygard (2016) for sub-national areas in Africa; Lee (2018) for North Korea.

@@

\bibitem{} Michalopoulos, Stelios, and Elias Papaioannou. 2013. ``Pre-Colonial Ethnic Institutions and Contemporary African Development.'' \textit{Econometrica}, 81(1): 113--152.
\bibitem{} Michalopoulos, Stelios, and Elias Papaioannou. 2014. ``National Institutions and Subnational Development in Africa.'' \textit{Quarterly Journal of Economics}, 129(1): 151--213.
